% Chapter Template

\chapter{Non-Abelian Gauge Theory} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 3. \emph{Non-Abelian Gauge Theory}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Yang-Mills Theory of non-Abelian gauge fields}

As we have already seen, a Lagrangian should remain invariant under global/local transformations. This means that the Lagrangian should have both global and local symmetries.

For spin-1 fields, like the electromagnetic field, U(1) symmetries exist. For other fields, such as the gluonic field for instance, SU(N) symmetry exists.

Let's consider one such system given by 


Let $\psi^{'} = U\psi$, $U \in SU(N)$. We can then say

\begin{equation}
L_{\psi^{'}} = \overset{_}{\psi}U^{-1}(i{\gamma^\mu}\partial_\mu-m)U\psi
\end{equation}
\begin{equation}
L_{\psi^{'}} = L_\psi + \overset{_}{\psi}U^{-1}(i{\gamma^\mu})\partial_\mu(U)\psi \\
\end{equation}
This hence warants the introduction of a new gauge field such that $L_{\psi^{'}} = L_\psi$

We introduce covariant derivative $D_{\mu}$, such that the modified Lagrangian is given by
\begin{equation}
{L} = \overset{_}{\psi}(i{\gamma^\mu}D_\mu-m)\psi
\end{equation}
$D_\mu = \partial_\mu +igT_{a}A^{a}_{\mu}$, where $g$ is coupling constant, $T_{a}$ are the generators of SU(N), and $A^{a}_{\mu}$ is the gauge field.

It can be proved that the this Lagrangian is invariant under SU(N), and the following condition is satisfied

\begin{equation}
T_{a}{A^{a}_{\mu}}^{'} = \frac{i}{g}(\partial_{\mu}U)U^{-1} + UT_{a}A^{a}_{\mu}U^{-1}
\end{equation}

We can account for this gauge field by introducing a pure gauge Lagrangian of the form of
\begin{equation}
	{L_{YM}}=-\frac{1}{4}{{F^a}_{\mu\nu}}{{F^{\mu\nu}_a}}
\end{equation}
where
\begin{equation}
	{{F^a}_{\mu\nu}}={\partial_\mu}{A^a}_\nu - {\partial_\nu}{A^a}_\mu -g{f_{abc}}{{A^b}_\mu}{{A^c}_\nu}
\end{equation}
Then, we can write the whole form of the Lagrangian as
\begin{equation}
{L} = \overset{-}{\psi}(i{\gamma^\mu}D_\mu-m){\psi} - \frac{1}{4}{{F^a}_{\mu\nu}}{{F^{\mu\nu}_a}}
\end{equation}

\section{Interactions of non-Abelian Gauge Fields}
On expanding equation (3.7) using $D_\mu = \partial_\mu +igT_{a}A^{a}_{\mu}$, we get

\begin{equation}
{L_{int}} = -g{\overset{-}{\psi}{T_a}{\gamma^\mu}{{A^a}_\mu}{\psi}
\end{equation}
This is the Lagrangian for the Yang-Mills Interaction between a Dirac Current due to charge $g$ and the Gauge Field.

Yang-Mills Theory is remarkable in the sense that it allows for an self-interacting term as $L_{YM}$ contains terms that interact amongst themselves. This means that the dynamics of the gauge bosons is much more complex than in QED as the bosons affect each other by their motion.

\section{Quantum Chromodynamics}
Non-Abelian gauge theories can describe most known interactions. $SU(3)$ symmetry gives rise to a theory called Quantum Chromodynamics, or QCD for short. A general $SU(N)$ symmetry has $(N^{2}-1)$ generators, and hence $SU(3)$ has 8 generators. Thus we can say that there are eight gauge fields, and the quanta of these fields are called gluons.